Aa Language Reference Manual

### 2019-04-20 v2/Ahir-asm/devel/docs/AaLRM.tex
Some major cleanups in handling WAR.  There seemed to be an unnecessary delay in the SCT -> UST dependency for WARs.
Also cleaned up the elaborate algorithm for Aa.  First parse
and then map is the approach to be used.  This was not
being followed completely.

Finally, do not delay WAR object refs.  Also, delete orphan
statements (unless qualified with $keep).  Checked on
some examples including AJIT CPU.

Issue remaining:  Combinational cycle delay introduced? Lets
check.
Added fifo mem with asynch read in queue implementation.

@@

>>>>

The {\bf Aa} compiler will optimize away dangling
assignment statements (whose targets are not
used any where in the program). In order to prevent
this from happening, you can use the \$keep keyword.
\begin{verbatim}
sacrifical_value := signal_from_somwhere $keep
\end{verbatim}
The \$keep keyword must be placed after the \$delay
keyword.

@@

\section{Synthetic instructions}

For convenience, there are some synthetic operations which
you can use to simplify coding an Aa program.  These
are listed below
\begin{itemize}
\item The \$reduce operation:
\begin{verbatim}
($reduce |  a  b  c)   
    (note: this is the same as  ((a+b)+c))
\end{verbatim}
Any associative operation may be used instead
of the or (add, mul, xor, and).
\item The \$split operation:  Suppose you want
to split a 32 bit variable into two 8-bit variables
and four 4-bit variables.  This can be done using
\begin{verbatim}
($split X 8 8 4 4 4 4) (a8 b8 c4 d4 e4 f4)
   (note: a8 := ($slice X 31 24) etc..)
\end{verbatim}
\item The \$concat operation:  This is the
reverse of a \$split.  
\begin{verbatim}
Y := ($concat a8 b8 c4 d4 e4 f4)
  (note: Y := (a8 && (b8 && (c4 && d4 ....))
\end{verbatim}
\item The \$excmux operations:  A multiplexor
whose selects are expected to be mutually exclusive.
\begin{verbatim}
Y := ($excmux s0 X0 s1 X1 s2 X2)
\end{verbatim}
This is equivalent to 
\begin{verbatim}
Y := ($reduce |
           ($mux s0 X0 0)
           ($mux s1 X1 0)
           ($mux s2 X2 0))
\end{verbatim}
Note that if all of s0,s1,s2 are 0, then
Y is assigned to 0.
\item The \$prioritymux operations:  A multiplexor
whose selects may not be mutually exclusive.
\begin{verbatim}
Y := ($prioritymux s0 X0 s1 X1 s2 X2
                $default 1)
\end{verbatim}
This is equivalent to 
\begin{verbatim}
Y := ($mux s0 X0
           ($mux s1 X1
                $mux s2 X2 1))
\end{verbatim}
\end{itemize}
